---
title: "Case Study"
output: html_document
date: "2023-10-10"
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(p8105.datasets)
library(tidyverse)
library(ggridges)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  rename(borough = neighbourhood_group, neighborhood = neighbourhood) |> 
  mutate(stars = review_scores_location/2)

```

# Brainstorm Questions
- Where are AirBnbs most expensive?
    - Borough? Neighborhood?
    - Do other factors (room type) affect price? What about rating?
- How long are AirBnbs active?
  - Are AirBnBs illegal and do they get shut down?
- Which units have the most avilability?
- How is review score impacted by location?

What boroughs have the most expensive AirBnBs?

```{r}
nyc_airbnb |>
  group_by(borough) |>
  summarize(
    mean_price = mean(price, na.rm = TRUE),
    med_price = median(price, na.rm = TRUE),
    min_price = mean(price, na.rm = TRUE),
    max_price = mean(price, na.rm = TRUE)
  )
```

Manhattan has both most expensive AirBnBs on average, and the max in the entire data set. Staten Island has a few exceptionally highly priced AirBnBs that pull it's mean above that of Brooklyn, though the latter has a higher median price. The lowest priced AirBnBs are in the Bronx.

What Manhattan neighborhoods have the most expensive AirBnBs?

```{r}
nyc_airbnb |>
  filter(borough == "Manhattan") |> 
  group_by(neighborhood) |>
  summarize(
    mean_price = mean(price, na.rm = TRUE),
    n_obs = n()
  ) |> 
  arrange(desc(mean_price))
```

Tribeca has the highest average AirBnB price, followed by the Flatiron District and NoHo.  

# Professor-Lead Analysis
```{r}
nyc_airbnb |> 
  count(borough)
```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```


```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) + 
  geom_histogram() +
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |>
  filter(price < 1000, room_type == "Entire home/apt") |>
  ggplot(aes(x = price)) + 
  geom_histogram() +
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  group_by(neighborhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)
  ) |> 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  mutate(neighborhood = fct_reorder(neighborhood, price)) |> 
  ggplot(aes(x = neighborhood, y = price)) +
  geom_boxplot()

```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  mutate(neighborhood = fct_reorder(neighborhood, price)) |> 
  ggplot(aes(x = price, y = neighborhood)) +
  geom_density_ridges()
```

# Making a Map
```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```


# Making a Map
```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |>
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = 0.5)
```





